Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-06 writeup/gz_hubble_data.tex

\begin{table*}
\center
\caption{Summary of Galaxy Zoo: Hubble imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   & 7336  \\
\hspace{10pt} \emph{GOODS-N}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S}  & $-$         & $-$                              & $-$  & $-$   & \emph{4785}  \\
\hline
total                         & $-$         & $-$                              & $-$  & 8310  & 113166  \\
\hline\hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\center
\caption{Summary of Galaxy Zoo: Hubble imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   &   \\
\hspace{10pt} \emph{GOODS-N~2~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S~2~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{3593}  \\
\hspace{10pt} \emph{GOODS-N~5~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{6015}  \\
\hspace{10pt} \emph{GOODS-S~5~epoch}  & $-$         & $-$                              & $-$  & $-$   & \emph{5142}  \\

\hline
total                         & $-$         & $-$                              & $-$  & 8310  & 130467  \\
\hline\hline
\end{tabular}
\end{table*}
